% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{etoolbox}
\usepackage{textcomp}
\usepackage{bm}
\robustify\cftdotfill


%-----------------------------------------------------------
%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars


%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.5in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7.5in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}


%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-4pt}}
\newcommand{\resheading}[1]{\vspace{1pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[7.25in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Corbin Taylor} & \textbf{\today} \\
Software Development Engineer and Astrophysicist &  \\
\end{tabular*}

\smallskip
\smallskip

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{Email}: cjtaylor2390@gmail.com & \textbf{LinkedIn}: https://www.linkedin.com/in/corbin-taylor/\\
\textbf{GitHub}: https://github.com/cjtaylor1990 & \\
\end{tabular*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Skills}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item \textbf{Front-End Technologies}: JavaScript (React, Redux, React Query, Jest, Cypress), Ruby, HTML, CSS
\item \textbf{Back-End Technologies}: Java (Spring Boot, JUnit, Mockito), Python (NumPy, SciPy), C++, C, SQL, MongoDB, Kafka
\item \textbf{Cloud Technologies}: AWS (S3, EC2, ECS, Lambda, RDS, DynamoDB), Docker, Kubernetes
\item \textbf{Operating Systems, Servers, \& Networking}: CLI, Shell scripting, Linux, OS X
\item \textbf{Leadership \& Communication}: Project planning, task delegation, collaborative problem solving, public speaking, and mentoring.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Work Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ressubheading{Capital One - Retail Bank Technology}{Nov 2022 - Present}{Software Development Engineer}{}
\begin{itemize}
	\resitem{Maintained Java Spring Boot and Kafka microservices on ECS and EC2 that consumed and published data for millions of financial transactions per day.}
	\resitem{Migrated consumer-facing API from a managed solution (ECS and RDS) to serverless (Lambda and DynamoDB).}
	\resitem{Automated team deployment processes that allowed for continuous delivery and reduced overhead for our legacy systems.}
	\resitem{Quickly remediated critical service vulnerabilities, securing sensitive customer data.}
	\resitem{Performed operations and development work that ensured our services were compliant with Federal regulation.}
	\resitem{Participated in team on-call rotation, mitigating problems quickly and minimizing customer impact.}
	\resitem{Mentored new and junior team members, helping them become familiar with team-specific technologies and best practices.}
	\resitem{Coordinated with third-party venders and led cross-team collaborations.}
\end{itemize}
\ressubheading{Amazon Web Services - AWS Security}{Jun 2020 - Nov 2022}{Software Development Engineer}{}
\begin{itemize}
	\resitem{Developed and maintained a mission-critical service used by tens-of-thousands of AWS employees to manage one million active AWS accounts.}
	\resitem{Contributed to the development and testing of a single-page web React-Redux application, as well as to the Java Spring and SQL backend.}
	\resitem{Initiated and led cross-team security improvement efforts, including migrating a Python-based auditing tool to native AWS.}
	\resitem{Researched and created recommendations for the handling of critical cryptographic credentials.}
	\resitem{Primary point of contact for collaboration between my service team and security auditing teams.}
	\resitem{Participated in the on-call rotation, root-causing and mitigating problems in a high-pressure environment.}
\end{itemize}
\ressubheading{University of Maryland - Department of Astronomy}{Jun 2014 - Jun 2020}{Graduate Research Assistant}{}
\begin{itemize}
	\resitem{Researched the properties of supermassive black holes and the Milky Way using computer simulations.}
	\resitem{Independently wrote scientific simulation and analysis software using Python and C++.}
	\resitem{Published multiple peer-reviewed articles in internationally-recognized scientific journals.}
	\resitem{Presented my work at professional conferences and universities in the US and Europe.}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Leadership Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ressubheading{AWS Summer Software Development Internship}{May 2022 - Aug 2022}{Lead Mentor}{}
\begin{itemize}
	\resitem{Led meetings with software development intern 3 times per week where I would work to disambiguate goals, define action items, and develop Agile strategies to deliver results.}
	\resitem{Helped intern onboard to my team's tech stack and familiarize themselves with the internal AWS ecosystem.}
	\resitem{Gave constructive feedback to helped the intern's professional development and overcome initial setbacks.}
\end{itemize}
\smallskip
\ressubheading{GRAD-MAP Diversity Program}{May 2014 - Aug 2017}{Team Member}{}
\begin{itemize}
	\resitem{Led the preparation and teaching of a multi-day Python workshop.}
	\resitem{Helped prepare and manage week-long research workshops that helped minority students develop skills necessary for a STEM career.}
	\resitem{Collaborated with minority-serving universities and colleges in Maryland, Virginia, and D.C.}
\end{itemize}
\smallskip
\ressubheading{University of Maryland - Department of Astronomy}{Aug 2013 - May 2014}{Graduate Teaching Assistant}{}
\begin{itemize}
	\resitem{Led 50 minute discussions with hands-on demonstrations for two sections once a week with an average of 20-30 students per section.}
	\resitem{Mentored struggling students during and outside of my weekly office hours.}
	\resitem{Graded homework, in-class assignments, and exams in a fair and timely manner.}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\ressubheading{University of Maryland}{College Park, MD}{Ph.D. Candidate Astronomy \& M.S. Astronomy}{2013-2021}
\begin{itemize}
	\resitem{PhD unfinished due to COVID-19 and changing professional priorities.}
\end{itemize}
\smallskip
\ressubheading{University of Toledo}{Toledo, OH}{B.S. Astrophysics \& B.S. Pure Mathematics}{2008-2013}
\begin{itemize}
	\resitem{Cumulative GPA: 3.81}
	\resitem{Graduated Magna Cum Laude with Physics Departmental Honors}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Select Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\resitem{Taylor, C. and Reynolds, C.S. 2018b; {\it X-Ray Reverberation From Black Hole Accretion Disks With Realistic Geometric Thickness}, ApJ, 868, 109}
	\resitem{Taylor, C. and Reynolds, C.S. 2018a; {\it Exploring The Effects of Disk Thickness On The Black Hole Reflection Spectrum}, ApJl, 855, 120}
	\resitem{Taylor, C.; Boylan-Kolchin, M.; Torrey, Paul; Vogelsberger, Mark; and Hernquist, Lars 2016; {\it The Mass Profile Of The Milky Way To The Virial Radius From The Illustris Simulation}, MNRAS 461, 3483}
\end{itemize}

\end{document}
